The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\*[-8pt] for the free eLearning program CrypTool (version 1.4.00)} \vspace{60pt}

### 2007-04-23 script/en/script-en.tex
be changes dated 2006-04-09 2006-04-11 2006-05-05 2006-05-30 2006-07-26

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ 
	The CrypTool Script: \\
	Mathematics and Cryptography \\
        \vspace{30pt}
        {\large	Background reading\\*[-8pt] 
        for the free elearnig program CrypTool (version 1.3.10)}
        \vspace{60pt}
}

@@

\author{
(c) Bernhard Esslinger (Co-author and editor), 1998-2005 \\
Frankfurt am Main
}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
\vspace{200pt}
This is a free document, so the content of the document can be copied and distributed,
also for commercial purposes; 
so long as the new version acknowledges author, title and the CrypTool web site. \\
Naturally, citations from the CrypTool script are possible, as in all other documents.
This licence is abutted on the GNU Free Documentation Licence.

@@

\newpage
\tableofcontents
\addcontentsline{toc}{section}{Contents}

@@

%\appendix \addcontentsline{toc}{section}{Appendix} %be_2005 raus
\begin{appendix}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
\end{appendix}

%\addcontentsline{toc}{section}{Index} %moved to style.ist
\printindex

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hack, damit Aufruf von \tableofcontents auch gleich \addcontentsline
% enthält. Damit steht im Inhaltsverzeichnis das Inhaltsverzeichnis
% mit korrekter Seitenzahl und Hyperlink.
\makeatletter
\renewcommand\tableofcontents{%
    \section*{\contentsname
        \@mkboth{%
           \MakeUppercase\contentsname}{\MakeUppercase\contentsname}}%
    \addcontentsline{toc}{section}{\contentsname}
    \@starttoc{toc}%
    }
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ 
	The CrypTool Script: \\
	Cryptography, Mathematics and more \\
        \vspace{30pt}
        {\large	Background reading\\*[-8pt] 
        for the free eLearning program CrypTool (version 1.4.00)}
        \vspace{60pt}
}

@@

\author{
(c) Bernhard Esslinger (co-author and editor), 1998-2006 \\
Frankfurt am Main, Germany
}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
\vspace{200pt}
This is a free document, so the content of the document can be copied and
distributed, also for commercial purposes -- as long as the author, title and
the CrypTool web site (www.cryptool.org) are acknowledged. \\
Naturally, citations from the CrypTool script are possible, as in all other
documents. This licence is abutted on the GNU Free Documentation Licence.

@@

\newpage
\tableofcontents  % --> is redefined !

@@

\begin{appendix}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
\end{appendix}

\printindex
